\documentclass[11pt]{report}
\usepackage{color}
\usepackage{hyperref}
\hypersetup{
  colorlinks = true
}
\pagenumbering{roman}
\topmargin=0.0in
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\marginparwidth=0.5in
\headheight=0pt
\headsep=0pt
\textheight=9.0in
\begin{document}

\centerline{{\LARGE \bf Atos Mentor Matching}}

\centerline{ \large \bf Biweekly Report 1, 12\textsuperscript{th} of October 2016}
\centerline{ Christopher Lau $\bullet$ Harry Chen $\bullet$ Matthew Bell }
\noindent
\line(1,0){470}\\


\noindent {\Large \bf Overview}
\smallskip

\noindent
This week consisted of building up connections between team members and establishing some of the platforms/frameworks that could be potentially used for development. The first meeting was also held with the client on 10/10/2016 to get a general overview of the project. Finally, an initial list of requirements was drafted.

\bigskip
\noindent{\Large \bf Meetings To Date}
\smallskip

\begin{description}
  \item[Meeting 1, 10\textsuperscript{th} of October 2016] --- In the meeting, our client (Jane Williams) explained to us the problem that the company (Atos) faced when matching mentors and mentees manually in her workplace. The client gave us a general overview of a solution to solve this problem which was an app to pair up mentors/mentees based on their expertise and also years in experience in thier workplace. An initial list of requirements was also drafted which were to be sent to the client to finalize by the end of the week.
  \item[Meeting 2, 11\textsuperscript{th} of October 2016] --- In this meeting, team members drafted some notes and a list of requirements which were to be sent to the client to be finalised. Team roles were also decided. Meeting ended with a discussion on plan for the next two weeks.
\end{description}

\bigskip
\noindent{\Large \bf Completed Tasks}
\smallskip

\noindent
Since the previous report these are the tasks that have been completed to date:
\begin{itemize}
  \item Set up a team meeting, meet each team members.
  \item Build connections (Trello, facebook group).
  \item Held a skype meeting with our client .
  \item Simple research for our project( mentor matching).
  \item Manage team roles for each member.
  \item Get basic requirements from client.
\end{itemize}

\bigskip
\noindent{\Large \bf Chris' Progress}
\smallskip

\noindent
Managed communication with client (i.e arranging meeting times). Researched about solutions to approach project and also technologies that should be used. Also worked on completing the bi-weekly report.\\

\bigskip
\noindent{\Large \bf Harry's Progress}
\smallskip

\noindent
Got the background resources from client and took a research on it. Compare different platforms that our app could be on. Took a meeting with client.\\

\pagebreak
\bigskip
\noindent{\Large \bf Matt's Progress}
\smallskip

\noindent
Took notes during initial client meeting and helped form the project requirements from this. Set up project tools (Git, Kanban board, virtual server) to assist later on, and researched the “Stable Marriage Problem”.\\

\noindent
Through my research I have determined that some of the aforementioned technologies would bring a tangible benefit to the development of the application and the end product. \\

\bigskip
\noindent{\Large \bf Problems To Resolve}
\smallskip

\noindent

\begin{itemize}
    \item Problems to be solved when making project website - e.g., acquiring project server from department.
    \item Research the matching examples from client and make a framework.
\end{itemize}

\bigskip
\noindent{\Large \bf Plan For The Next Two Weeks}
\smallskip

\noindent
Over the next two weeks we will be focusing on the following activities:

\begin{itemize}
 \item Take the mentor matching example from client
 \item Meet Mike (Chief Technology Officer) and get requirements from tech side
 \item Continue working on requirements and research.
 \item Existing / example code investigations should begin.
 \item Create project website for client, TAs and supervisor.
 \item Present Initial analysis of literature findings to client.
 \item with the research identifying strategies, ideas, tools, etc. Compare Software Engineering Methods
\end{itemize}

\end{document}
