\documentclass[11pt]{report}
\usepackage{color}
\usepackage{hyperref}
\hypersetup{
  colorlinks = true
}
\pagenumbering{roman}
\topmargin=0.0in
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\marginparwidth=0.5in
\headheight=0pt
\headsep=0pt
\textheight=9.0in
\begin{document}

\centerline{{\LARGE \bf Atos Mentor Matching}}

\centerline{ \large \bf Biweekly Report 3, 18\textsuperscript{th} of November 2016}
\centerline{ Christopher Lau $\bullet$ Harry Chen $\bullet$ Matthew Bell }
\noindent
\line(1,0){470}\\


\noindent {\Large \bf Overview}
\smallskip

\noindent
The first week consisted of scenario week where we were able to research different web frameworks such as Django, Ruby on Rails and PHP frameworks that we could use for our experiment logging tool. We had the chance to use some of the frameworks to implement a working web application which gave us some hands on experience with them. Also, we were required to deploy our web application automatically on a web server. The knowledge we gained through this will prove very useful when deploying our final prototype.\\

\noindent
After scenario week was reading week where user stories for the project were created and sketches of the user interface were created. We also conducted further design into the architecture of the system.\\

\bigskip
\noindent{\Large \bf Meetings To Date}
\smallskip

\noindent
Since the last two weeks are scenario week and reading week, we did not have meetings with the supervisor and the client.\\

\begin{description}
  \item[Team Meeting 4, 17\textsuperscript{th} of November 2016] --- We discussed the UI designs made by Harry, talked about some of the functions which need to be implemented inside the app, and confirmed questions to send to the client.
\end{description}

\bigskip
\noindent{\Large \bf Completed Tasks}
\smallskip

\noindent
Since the previous report these are the tasks that have been completed to date:
\begin{itemize}
  \item Create formal outline of project.
  \item Formalise architecture design and UI design.
  \item Finish research of similar existing systems.
  \item Take notes from documents that the client provided and created a user story.
  \item Add meeting minutes to website.
\end{itemize}

\bigskip
\noindent{\Large \bf Chris' Progress}
\smallskip

\noindent
For the last two weeks, I have created a document illustrating the user stories for the webapp and also containing notes from our last meeting with our client. I also continued to manage communication with our client updating her on our progress so far. Research regarding any similar products to Mentor Match app was also done.\\

\bigskip
\noindent{\Large \bf Harry's Progress}
\smallskip

\noindent
What I did last two weeks is took a research with existing prototypyes, \textbf{Mentor Match} and \textbf{Business mentoring}, wrote an article for reasearch of both apps, including what their matching based on, how they construct user information, and what we could learn form these apps. Also i finished formalised user interface design for our app (by sketch).\\

\bigskip
\noindent{\Large \bf Matt's Progress}
\smallskip

\noindent
As well as the scenario week work, I have worked on researching some of the possible technology stacks that we can use for our project, prioritising ease of use for both us and the client. I have also been designing the system architecture and am currently working on a rudimental matching algorithm that will match based on user tags.\\

\bigskip
\noindent{\Large \bf Plan For The Next Two Weeks}
\smallskip

\noindent
Over the next two weeks we will be focusing on the following activities:

\begin{itemize}
  \item Create personas and scenarios.
  \item Start working on constructing a first prototype.
  \item Validate the UI design and structure design with the client.
  \item Develop a first version of the matching algorithm.
  \item Research the framework and technologies we'll use for implementing our project.
  \item Work on adding more content to our project website regarding our progress so far.
\end{itemize}

\hrule

\subsection*{Keeping Up With The Project}

To complement these biweekly reports, you can also view these pages:\\

\noindent
Project site: http://students.cs.ucl.ac.uk/2016/group19/\\

\noindent
Code repository: https://github.com/mbellgb/syseng19-code\\

\noindent
Documentation: https://github.com/mbellgb/syseng19-docs

\end{document}
