\documentclass[11pt]{report}
\usepackage{color}
\usepackage{hyperref}
\hypersetup{
  colorlinks = true
}
\pagenumbering{roman}
\topmargin=0.0in
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\marginparwidth=0.5in
\headheight=0pt
\headsep=0pt
\textheight=9.0in
\begin{document}

\centerline{{\LARGE \bf Atos Mentor Matching}}

\centerline{ \large \bf Biweekly Report 3, 2\textsuperscript{nd} of December 2016}
\centerline{ Christopher Lau $\bullet$ Harry Chen $\bullet$ Matthew Bell }
\noindent
\line(1,0){470}\\


\noindent {\Large \bf Overview}
\smallskip

\noindent
Over the last two weeks, the team focused mainly on completing most of the research required for the final structure of the system. The research included which technologies to be used for developing the final system (which backend/frontend framework and libraries) and completed the matching algorithm design with pseudocode. A wireframe prototype was also created based on the sketches that were produced during the earlier stages of development. We have also been constantly updating and adding content to the project website based on the research we have done.

\bigskip
\noindent{\Large \bf Meetings To Date}
\smallskip

% Since our client replied our email for three weeks we can not set up meeting with her. Instead we could only continue other works that not require data from client.

\begin{description}
  \item[Team Meeting 5, 24\textsuperscript{th} of November 2016] --- In this meeting we discussed the research we collected about backend frameworks, and after voting we decided use Django and PostgreSQL for our system.
  \item[Team Meeting 6, 1\textsuperscript{st} of December 2016] --- In this meeting Harry brought his first interface design and each team member gave feedback on it. Also, we discussed (and voted for) which frontend framework we're going to use for the prototype, deciding to use AngularJS plus Ionic.
\end{description}

\bigskip
\noindent{\Large \bf Completed Tasks}
\smallskip

\noindent
Since the previous report these are the tasks that have been completed to date:
\begin{itemize}
    \item Conduct tech stack research
    \item Create report on collaboration
    \item Create draft (pseudocode) matching algorithm
    \item Create first interface mockup
    \item Uploade project’s requirements and background on website
\end{itemize}

\bigskip
\noindent{\Large \bf Chris' Progerss}
\smallskip

\noindent
For the last two weeks, I have been in charge of mainly updating content to the project website and structuring it in a orderly, neat and readable format. Research on frontend technologies that could be used for the final system was also done. I have also created a general outline of what is to be included in our project website based on the sample websites provided.\\

\bigskip
\noindent{\Large \bf Harry's Progress}
\smallskip

\noindent
In last two weeks I did a research for front-end framework we going yo use for project, AngularJS and Ionic, which is used for building web app. Also I did a summary of colboraition, created first version of project’s prototype based on UI framework design.\\

\bigskip
\noindent{\Large \bf Matt's Progress}
\smallskip

I created the first version of the main matching system's user flow and algorithm, as well as explored possible tech stacks for us to use. I also spent a little time researching into how we could experiment, and how we can measure results.

\noindent
Since the last report I have been focusing my efforts on researching the potential technologies for the project. \\

\noindent
Through my research I have determined that some of the aforementioned technologies would bring a tangible benefit to the development of the application and the end product. \\

\bigskip
% \noindent{\Large \bf Problems To Resolve}
% \smallskip
%
% \noindent
% Not many problems have been encountered, however the following need to be addressed:
%
% \begin{itemize}
%   \item {\it Problem 1\/} --- This could be solved by implementing x.
%   \item {\it Problem 2\/} --- We could lessen this problem by using y to communicate more.
%   \item {\it Problem 3\/} --- This should be avoided by ensuring that everyone is familiar and up to speed with our chosen source control \href{http://git-scm.com}{Git}.
% \end{itemize}
%
% \bigskip
\noindent{\Large \bf Plan For The Next Two Weeks}
\smallskip

\noindent
Over the next two weeks we will be focusing on the following activities:

\begin{itemize}
    \item Get our client’s reply and set up a meeting.
    \item Create personas,scenarios and use cases.
    \item Do evaluation and test for prototype.
    \item Set up project code structure.
    \item Finish all documentation required for website.
    \item Get feedback for website from our TA.
\end{itemize}

\hrule

\subsection*{Keeping Up With The Project}

To complement these biweekly reports, you can also view these pages:\\

\noindent
Project site: http://students.cs.ucl.ac.uk/2016/group19/\\

\noindent
Code repository: https://github.com/mbellgb/syseng19-code\\

\noindent
Documentation: https://github.com/mbellgb/syseng19-docs

\end{document}
