\documentclass[11pt]{report}

\begin{document}
    \centerline{\LARGE \bf System Requirements}

    \section*{Must-Have Requirements}
    \begin{itemize}
        \item \textbf{Matching system} --- there must be a matching algorithm that matches mentors and mentees as best as possible according to their preferences.
        \item \textbf{Preferences for matching} --- there must be a system for mentors and mentees to specify their preferences for matching, for instance interests.
        \item \textbf{Separate mentorship programmes} --- the system must allow for a number of separate mentorship programmes with their own matching constraints.
        \item \textbf{Personal status} --- users must be able to see the status of their mentorships, for instance whether they can match with users and how active the mentorship is.
        \item \textbf{Web app} --- the app must be able to be accessed on both mobile and desktop form factors.
    \end{itemize}

    \section*{Should-Have Requirements}
    \begin{itemize}
        \item \textbf{Profile system} --- users should be able to create and manage a simple profile so that other users can learn about them. Should include name, image and perhaps a short bio.
        \item \textbf{Notifications} ---  users should be able to receive notifications about key features of the app, for instance when matches are allocated. Should work across different form factors.
        \item \textbf{Admin bulk operation interface} --- there should be an interface that allows admins to perform bulk create/read/update/destroy (CRUD) operatons easily.
    \end{itemize}

    \section*{Could-Have Requirements}
    \begin{itemize}
        \item \textbf{Mentorship meeting record} --- the app could be able to store records of the mentor and mentee meeting each other during the course of the mentorship, with the ability to add comments to this.
        \item \textbf{Notifications to meet} --- the app could prompt mentors to meet with their mentee after a period of inactivity, for instance two weeks.
        \item \textbf{Instant messaging} --- the app could facilitate instant messaging between mentors and mentees.
    \end{itemize}

    \section*{Would-Have Requirements}
    \begin{itemize}
        \item \textbf{Corporate Directory Lookup} --- the app would be able to use the company's internal ``Corporate Directory'' to populate users' profiles.
    \end{itemize}
\end{document}
